%\chapter{Introduction}

%\section{Background and Recent Research}
%\subsection{<any sub section here>}

%\subsection{Literature Survey}

%\subsubsection{<Sub-subsection title>}
%some text\cite{citation-1-name-here}, some more text

%\subsubsection{<Sub-subsection title>}
%even more text\footnote{<footnote here>}, and even more.

\section{Motivation}

This report will provide a detailed account of the processes our group
used to design and implement a database that can be used to manage
a blood donation system. Each subsection of the report will correspond to an
important feature of database design.

\section{Requirement Analysis}

\subsection{Features of Front End}
\begin{itemize}
  \item Complete and comprehensive information about the process of blood donation.
  \item Details about the blood donors including their name, eligibility for donation and their blood group.
  \item admin is the main authority who can do addition, deletion, and modification if required.
\end{itemize}

\subsection{Functions of Database}
\break
\textbf{BLOOD DONORS}
\begin{itemize}
  \item Login ID and password to update their personal information.
  \begin{itemize}
    \item Phone Numbers
    \item Address
    \item Password
    \item Status
  \end{itemize}
  \item Access to their blood donation History.
  \item Ability to get a certificate for their donation.
  \item Current blood donation status, including remainder every six months.
  \item Ability to receive payment for their blood donations.
\end{itemize}

Note that, the admins can also donate blood.

\textbf{ADMIN}
\begin{itemize}
  \item Same as functions for BLOOD DONORS, plus
  \item Add new donors.
  \item Remove donors.
  \item Manage the entire database.
  \item Modify blood donor details.
  \item Handle payments if and when necassary.
  \item Give out certificates to all blood donors.
  \item Maintain and keep track of organisations that help sustain the blood donation campaign.
  \item View all donor information except passwords.
\end{itemize}

\textbf{HELPING ORGANIZATIONS}
\begin{itemize}
  \item unique ID
  \item History of monetary help
  \item Frequency of payments
  \item Organization Incharge
  \item Start Date
\end{itemize}

\textbf{BLOOD DONATION CENTRE EMPLOYEE}
\begin{itemize}
  \item Employee ID
  \item Centre ID
  \item First Name
  \item Last name
  \item Role
  \item Salary
  \item Address
  \item Phone number
\end{itemize}

\textbf{BLOOD DONATION CENTRES}
\begin{itemize}
  \item Centre ID
  \item Locations
  \item Affliated To
  \item Date of Affliation
  \item Affliation ID
   \item status
 \item descriptive attributes
 \item Opening time
 \item Closing time
\end{itemize}

\textbf{BLOOD REQUESTS}
\begin{itemize}
  \item Blood Type required
  \item Name of Blood Donee
  \item Address of Blood Donee
  \item Date and Time of request
  \item Payment made (if any)
\end{itemize}
